| Base de datos de abejas ibéricas \n| Iberian bees database\n

### 2022-07-01 Manuscript/manuscript.Rmd
Update on manuscript figures

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap="\\textbf{Figure 1}",out.width="70%"}
# code courtesy of Paco Rodriguez.
library(sf)
library(raster)
library(rasterVis)
library(tidyverse)
crs.geo <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
crs.laea <- "+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

library(data.table)
data <- read.table("../Data/iberian_bees.csv.gz", header = T, quote = "\"", sep = ",")

@@

datos.sf <- st_as_sf(dat,
                     coords = c("Longitude", "Latitude"),
                     crs = crs.geo
)

datos.laea <- st_transform(datos.sf,
                           crs = crs.laea
)

ras <- raster(datos.laea, resolution = 10000)

ras.counts <- rasterize(datos.laea[, "Accepted_name"], ras,
                        field = "Accepted_name", fun = "count"
)

levelplot(log(ras.counts+1), margin = FALSE, scales = list(draw = FALSE),
          par.settings = viridisTheme())

@@

```{r echo=FALSE, fig.align='center', out.width="70%", fig.cap="\\textbf{Figure 2}"}
# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10, face = "italic"),   axis.title=element_text(size=16)) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="\\textbf{Figure 3}", message=FALSE, warning=FALSE, cache=FALSE, fig.width=5}
# Prepare top 20 records
by_year <- data %>% filter(!Accepted_name == "Apis mellifera")

p1 <- ggplot(by_year, aes(Year)) +
  geom_histogram(fill = "#287D8EFF") +
  theme_classic() +
  ylab("Number of records") +
  scale_y_continuous(expand = c(0, 0)) + ggtitle("A") + theme(axis.title=element_text(size=12))

@@

p2 <- ggplot(data = month_sum, aes(x = month_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  scale_y_continuous(expand = c(0, 0)) +
  ylab("Number of records") +
  xlab("Months") + ggtitle("B") + theme(axis.title=element_text(size=12))

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center',out.width="115%"}
library(sf)
library(raster)
library(rasterVis)
library(tidyverse)
library(data.table)
data <- read.table("../Data/iberian_bees.csv.gz", header = T, quote = "\"", sep = ",")

@@

# install.packages("ggplot2")
library(ggplot2)
library(viridis)
library(giscoR) #map of europe
library(ggspatial)

#gisco
#gisco_countrycode
eu2016 <- c(gisco_countrycode[gisco_countrycode$eu, ]$CNTR_CODE)

#Select data
europe_map <- gisco_get_nuts(
  year = "2016",
  epsg = "3035",
  resolution = "3",
  nuts_level = "2",
  country = eu2016) %>%
  sf::st_transform(crs = 4326)

# Borders
borders <- gisco_get_countries(
  epsg = "3035",
  year = "2016",
  resolution = "3",
  country = eu2016) %>%
  sf::st_transform(crs = 4326)

vars <- c("ES",  "PT")
#Extract counties of interest
euro_map <- filter(europe_map, CNTR_CODE %in% vars)

#Plot map
world <- map_data("world")

library(ggsn)

ibera <- world %>% filter(region == "Spain" | region == "Portugal"| region == "France" |region == "Andorra"|region == "Marroco")

ggplot(data=dat, aes(Longitude, Latitude)) +
geom_map(data = ibera, map = ibera,
aes(long, lat, map_id = region), color = "white", fill = "grey", size = 0.1) +
geom_bin2d(bins=70, aes(fill=log(..count..))) +
theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
size = 0.5), panel.background = element_rect(fill = "aliceblue"),
panel.border = element_rect(colour = "black", fill=NA, size=1.5)) +
scale_fill_viridis() +
coord_sf(xlim = c(-9, 4), ylim = c(36, 44)) +
ggsn::north(x.min = -0.7, x.max = 3.3, 
y.min = 35.6, y.max = 37.6, scale = 0.4) +
scalebar(x.min = -2, x.max = 3.6,
y.min = 36.5, y.max = 42.5,
dist = 100, dist_unit = "km",st.size = 3,st.dist=0.04,
transform = TRUE, model = "WGS84", st.color="black") +
theme(axis.title = element_text(size=16), axis.text = element_text(size=12))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', out.width="100%"}

data <- read.table("../Data/iberian_bees.csv.gz", header = T, quote = "\"", sep = ",")

# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11, face = "italic"), axis.text.y = element_text(size = 12),
  axis.title=element_text(size=16), axis.line =element_line(size=1)) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

```{r echo=FALSE, warning=FALSE, message=FALSE,fig.width=7,fig.height=6, fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, out.width="100%"}

library(tidyverse)
data <- read.table("../Data/iberian_bees.csv.gz", header = T, quote = "\"", sep = ",")

# Prepare top 20 records
by_year <- data %>% filter(!Accepted_name == "Apis mellifera")

p1 <- ggplot(by_year, aes(Year)) +
  geom_histogram(fill = "#287D8EFF") +
  theme_classic() +
  ylab("Number of records") +
  scale_y_continuous(expand = c(0, 0)) + ggtitle("A") + theme(axis.title=element_text(size=16), axis.text =element_text(size=12), axis.line =element_line(size=1),
plot.title = element_text(size=18, face = "bold"))

@@

p2 <- ggplot(data = month_sum, aes(x = month_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  scale_y_continuous(expand = c(0, 0)) +
  ylab("Number of records") +
  xlab("Months") + ggtitle("B") + theme(axis.title=element_text(size=16), axis.text =element_text(size=12), axis.line =element_line(size=1),
plot.title = element_text(size=18, face = "bold"))
